Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-17 VegOzone.tex
Added biomass reduction

The estimated biomass reduction in \unit{\%} due to \chem{O_3} following \citet{ICP:MappingManual2017} is shown in Table~\ref{tab:biomass_reduction}. {\bf TODO: Lisa? Add paragraph about biomass reduction to introduction?}

\begin{table}[t]
  \caption{Estimated total biomass reduction in \unit{\%} due to \chem{O_3} following \citet{ICP:MappingManual2017}.}
  \label{tab:biomass_reduction}
\begin{tabular}{lccrr}
\tophline
Year & \multicolumn{4}{c}{PFT}\\
& Downy birch & Norway spruce & \multicolumn{2}{c}{Perennial grassland}\\
\middlehline
2018 & 11.99 & 2.34 & 8.06 & 10.51$^*$\\
2019 & 10.07 & 2.26 & 6.43 & 7.90$^*$\\
clim. & 13.81 & 2.58 & 6.67 & 8.29$^*$\\
\bottomhline
\end{tabular}
\belowtable{$^*$ above ground biomass} % Table Footnotes
\end{table}

>>>>

The estimated biomass reduction in \unit{\%} due to \chem{O_3} for bespoke type boreal in accordance to \citet{ICP:MappingManual2017, ESPR:Hayes2021} is shown in Table~\ref{tab:biomass_reduction}. The estimated uncertainies correspond to a $\pm 20\,\unit{\%}$ variation in light threshold and SWP=on. {\bf TODO: Lisa? Add paragraph about biomass reduction to introduction?}

\begin{table}[t]
  \caption{Estimated total biomass reduction in \unit{\%} due to \chem{O_3} for bespoke type boreal. Uncertainies correspond to a $\pm 20\,\unit{\%}$ variation in light threshold and SWP=on.}
  \label{tab:biomass_reduction}
\begin{tabular}{lllll}
\tophline
Year & \multicolumn{4}{c}{PFT}\\
& Downy birch & Norway spruce & \multicolumn{2}{c}{Perennial grassland}\\
\middlehline
2018 & $15.5^{+(1.9...2.1)}_{-(0.8...1.5)}$ & $2.5^{+(0.2)}_{-(0.2)}$ & $9.7^{+(0.2)}_{-(0.2)}$ & $^*13.1^{+(0.3)}_{-(0.3)}$\\
2019 & $17.4^{+(2.5)}_{-(1.8)}$ & $3.0^{+(0.2)}_{-(0.3)}$ & $10.5^{+(0.1...0.2)}_{-(0.0...0.1)}$ & $^*14.5^{+(0.2...0.3)}_{-(0.1...0.3)}$\\
\bottomhline
\end{tabular}
\belowtable{$^*$ above ground biomass} % Table Footnotes
\end{table}
